A preliminary constraint grammar for Russian

### 2015-02-10 2015-nodalida-ruscg/ruscg.tex
add a cite
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58652 72bbbca6-d526-0410-a7d9-f06f51895060
add layout
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58656 72bbbca6-d526-0410-a7d9-f06f51895060
error categorisation
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58669 72bbbca6-d526-0410-a7d9-f06f51895060
rule types
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58673 72bbbca6-d526-0410-a7d9-f06f51895060
add comment
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58676 72bbbca6-d526-04

\newcommand{\ft}[1]{\marginpar{\scriptsize F: #1}} % Fran's comments
\newcommand{\rr}[1]{\marginpar{\scriptsize R: #1}} % Rob's comments
\newcommand{\cw}[1]{\marginpar{\scriptsize W: #1}} % Cute wife's comments
\newcommand{\dm}[1]{\marginpar{\scriptsize D: #1}} % Detmar's comments
\newcommand{\lj}[1]{\marginpar{\scriptsize L: #1}} % Laura's comments

@@

\author{Author1 \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain.com} \\\And
  Author2 \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain.com} \\}

\date{2015}

\begin{document}
\maketitle
\begin{abstract}
  Hargle bargle
\end{abstract}

@@

>>>>

\newcommand{\ft}[1]{\marginpar{\scriptsize F: #1}} % Fran's comments
\newcommand{\rr}[1]{\marginpar{\scriptsize R: #1}} % Rob's comments

@@

\author{Francis M. Tyers \\
  HSL-fakultehta, \\
  UiT Norgga árktalaš universitehta, \\
  N-9018 Romsa \\
  {\tt francis.tyers@uit.no} \\\And
  Robert Reynolds \\
  HSL-fakultehta, \\
  UiT Norgga árktalaš universitehta, \\
  N-9018 Romsa \\
  {\tt robert.reynolds@uit.no} \\}

% \author{Author1 \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain.com} \\\And
%   Author2 \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain.com} \\}
% 
\date{2015}

\begin{document}
\maketitle
\begin{abstract}
 This paper presents preliminary work on a constraint
 grammar based disambiguator for Russian. Russian is
 a Slavic language with a high degree of both in-category
 and out-category homonymy in the inflectional system.
 The pipeline consists of a finite-state morphological
 analyser and constraint grammar. The constraint 
 grammar is tuned to be high recall at the expense of 
 low precision.
\end{abstract}

@@

\cite{Karlsson-90}

\section{Review of literature}
% ROB + FRAN
% different CGs 
% faroese
% estonian
%

\cite{trosterud2009}

\section{Ambiguity in Russian}

\section{Pipeline}

\subsection{Morphological analyser}
% ROB

\subsection{Disambiguation rules}

\begin{table}
  \begin{tabular}{lrrr}
    \hline
         & {\sc select} & {\sc remove} & {\sc map} \\
    \hline
  \end{tabular}
\end{table}

\section{Development process}

\subsection{Combining with a statistical tagger}

\section{Evaluation}

\begin{table}
  \begin{tabular}{|l|r|r|}
    \hline
    Missing lexeme & &  \\          % безбалластный, FALSENEG: Кий<np><ant><m><sg><ins> ['кий<n><m><nn><sg><ins>']
    Partial lexeme & &  \\          % франко-норманнское
    Missing analysis & &  \\        % 
    Equally valid analysis & & \\   % большой<adj><comp><pred> ['больше<adv>'] (?)
    Correct reading removed & &  \\ % 
    \hline
  \end{tabular}

\end{table}

% unknown words from test corpus, categorisation

% rule error analysis

\section{Future work}

% func analysis
% dep analysis
